Optimal (Multiway) Spatial Joins

### 2024-05-23 msj.tex
yufei

\begin{figure*}
    \begin{tabular}{ccc}
        \includegraphics[height=30mm]{./artwork/prob-a} & 
        \hspace{3mm}
        \includegraphics[height=30mm]{./artwork/prob-b} &
        \hspace{3mm}
        \includegraphics[height=30mm]{./artwork/prob-c} \\
%         &
%         \hspace{3mm}
%         \includegraphics[height=30mm]{./artwork/prob-d} \\
        (a) Problem $\EuScript{A}$ and $\EuScript{D}$ &
        \hspace{3mm}
        (b) Problem $\EuScript{B}$ &
        \hspace{3mm}
        (c) Problem $\EuScript{C}$
%         &
%         \hspace{3mm}
%         (d) Problem $\EuScript{D}$
    \end{tabular}

@@

\begin{lemma} \label{sec:hv:type1:proj}
    A $(k-2)$-tuple $(r_1', r_2, ..., r_k)$ exists in $\J(R_1', R_2, ..., R_{k-2})$ if and only if the $(k-2)$-tuple $(r_1, r_2, ..., r_k)$ exists in $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$, where $r_1$ is the rectangle in $R_1$ defining $r_1'$.
\end{lemma}

@@

>>>>

\begin{figure*}
    \begin{tabular}{ccc}
        \includegraphics[height=30mm]{./artwork/prob-a} & 
        \hspace{3mm}
        \includegraphics[height=30mm]{./artwork/prob-b} &
        \hspace{3mm}
        \includegraphics[height=30mm]{./artwork/prob-c} \\
%         &
%         \hspace{3mm}
%         \includegraphics[height=30mm]{./artwork/prob-d} \\
        (a) Problems $\EuScript{A}$ and $\EuScript{D}$ &
        \hspace{3mm}
        (b) Problem $\EuScript{B}$ &
        \hspace{3mm}
        (c) Problem $\EuScript{C}$
%         &
%         \hspace{3mm}
%         (d) Problem $\EuScript{D}$
    \end{tabular}

@@

\begin{lemma} \label{lmm:hv:type1:proj}
    A $(k-2)$-tuple $(r_1', r_2, ..., r_k)$ exists in $\J(R_1', R_2, ..., R_{k-2})$ if and only if the $(k-2)$-tuple $(r_1, r_2, ..., r_k)$ exists in $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$, where $r_1$ is the rectangle in $R_1$ defining $r_1'$.
\end{lemma}

The proof is presented in Appendix~\ref{app:lmm:hv:type1:proj}. Note that the size of $\Pi_{1:k-2}(\J_1(R_1, ...,$ $R_{k-2}, H, V))$ is bounded by that of $\J_1(R_1, ..., R_{k-2}, H, V)$, which in turn is bounded by $\out$. Thus, as a corollary of Lemma~\ref{lmm:hv:type1:proj}, the $(k-2)$-SJ instance $R_1', R_2, ..., R_{k-2}$  can be settled in $F_{k-2}(n, \out)$ time using $G_{k-2}(n, \out)$ space.

@@

\section{Proof of Lemma~\ref{lmm:hv:type1:proj}} \label{app:lmm:hv:type1:proj}
